### 2018-04-15 tex/paper.tex
Added discussion of where to end of section 5

The next primitive, \haskellinline{When}, waits for one of three things to happen:
\begin{enumerate}
 \item Two out of three choose $0$, for \haskellinline{pay}. 
 \item Two out of three choose $1$, for \haskellinline{refund}.
 \item The block 90 is added to the blockchain.
\end{enumerate}

@@

>>>>

The next primitive, \haskellinline{When}, waits for one of three things to happen:
\begin{enumerate}
 \item Two out of three choose $0$, for `\haskellinline{pay}'. 
 \item Two out of three choose $1$, for `\haskellinline{refund}'.
 \item The block 90 is added to the blockchain.
\end{enumerate}

@@

Reflecting on the example we can see that using Haskell definitions has made the contract substantially more comprehensible; it will also support more efficient operation, if we were to replace the repeated  expression \haskellinline{two_chose 1 2 3 1} above by a \haskellinline{where} clause, 
\begin{haskellcode}
escrow = ...
                    (When (OrObs (two_chose 1 2 3 0)
                                 chose_refund)
                          90
                          (Choice chose_refund
                           ...
         ...
         where 
         chose_refund = two_chose 1 2 3 1                 
\end{haskellcode}
then the repeated computation of the expression will be avoided.
